### 2014-11-12 tex/intro.tex
precision

In this work, we present a technique for heap summarization,
initialization, and analysis in the context of symbolic execution. We
represent the heap as a bipartiate graph of references and sets of
constraints over locations. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of
objects, allowing us to handle aliasing and (ii) it does not require
rewrite of the constraints during updates to the heap nor does it
introduce any auxillary variables in the constraints. During symbolic
execution, we initialize, summarize, and update the bipartiate
graph. Unlike GSE, however, the heaps are partitioned only at points
of divergence in the control flow graph. These points of
non-determinism are at field accesses that lead to null-pointer
exceptions and at comparisons of references. The former represents a
divergence due to exceptional control flow while the later due to
program structure.

@@

>>>>

In this work, we present a technique for heap summarization,
initialization, and analysis in the context of symbolic execution. We
represent the heap as a bipartiate graph of references and sets of
constraints over locations. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of
objects, allowing us to handle aliasing and (ii) it does not require
rewrite of the constraints during updates to the heap nor does it
introduce any auxillary variables in the constraints. During symbolic
execution, we initialize, summarize, and update the bipartiate
graph. Unlike GSE, however, the heaps are partitioned only at points
of divergence in the control flow graph. These points of
non-determinism are at field accesses or writes that lead to
null-pointer exceptions and at comparisons of references. The former
represents a divergence due to exceptional control flow while the
later due to program structure.

@@

The heap summary approach for symbolic execution is sound and complete
with respect to anything you can prove using a GSE machine. We should
the existence of a bi-simulation relation. In other words, any
property that can be proved using GSE can also be proved using heap
summaries, furthermore, any property proved by heap summaries can also
be proved by GSE---given the same bounds on heap reference chains and
loops.

%preserves the heap
%configurations and program behaviors

%complete --> anything prove with GSE you can with heap sound -->
%preserves the same behaviors in the GSE machine.
